Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-14 icse/paper.tex
Finish up relations

\subsubsection{Relation}
Clone instances in a clone class can have a relation with each other through inheritance. This relation has a big impact on how the clone should be refactored \cite{fontana2015duplicated}. We define the following categories to map the relation between clone instances in a clone class. These categories do not map external classes (classes outside the project, for instance belonging to a library) unless explicitly stated:
\begin{itemize}
    \item \textbf{Common Class}: All clone instances are in the same class.
    \begin{itemize}
        \item \textbf{Same Method}: All clone instances are in the same method.
        \item \textbf{Same Class}: All clone instances are in the same class.
    \end{itemize}
    \item \textbf{Common Hierarchy}: All clone instances are in the same inheritance hierarchy.
    \begin{itemize}
        \item \textbf{Superclass}: Clone instances reside in a class or its parent class.
        \item \textbf{Sibling Class}: All clone instances reside in classes with the same parent class.
        \item \textbf{Ancestor Class}: All clone instances reside in a class, or any of its recursive parents.
        \item \textbf{First Cousin}: All clone instances reside in classes with the same grandparent class.
        \item \textbf{Same Hierarchy}: All clone instances are part of the same inheritance hierarchy.
    \end{itemize}
    \item \textbf{Common Interface}: All clone instances are in classes that have the same interface.
    \begin{itemize}
        \item \textbf{Same Direct Interface}: All clone instances are in a class that have the same interface.
        \item \textbf{Same Class}: All clone instances are in an inheritance hierarchy that contains the same interface.
    \end{itemize}
    \item \textbf{Unrelated}: All clone instances are in classes that have the same interface.
    \begin{itemize}
        \item \textbf{No Direct Superclass}: All clone instances are in classes that have the Object class as parent.
        \item \textbf{No Indirect Superclass}: All clone instances are in a hierarchy that contains a class that has the Object class as parent.
        \item \textbf{External Superclass}: All clone instances are in classes the same external class as parent.
        \item \textbf{Indirect External Ancestor}: All clone instances are in a hierarchy that contains a class that has an external class as parent.
    \end{itemize}
\end{itemize}

>>>>

\subsubsection{Relation}
% The rationale for our categories regarding clone relations.
Clone instances in a clone class can have a relation with each other through inheritance. This relation has a big impact on how the clone should be refactored \cite{fontana2015duplicated}. We define the following categories to map the relation between clone instances in a clone class. These categories do not map external classes (classes outside the project, for instance belonging to a library) unless explicitly stated:
\begin{itemize}
    \item \textbf{Common Class}: All clone instances are in the same class.
    \begin{itemize}
        \item \textbf{Same Method}: All clone instances are in the same method.
        \item \textbf{Same Class}: All clone instances are in the same class.
    \end{itemize}
    \item \textbf{Common Hierarchy}: All clone instances are in the same inheritance hierarchy.
    \begin{itemize}
        \item \textbf{Superclass}: Clone instances reside in a class or its parent class.
        \item \textbf{Sibling Class}: All clone instances reside in classes with the same parent class.
        \item \textbf{Ancestor Class}: All clone instances reside in a class, or any of its recursive parents.
        \item \textbf{First Cousin}: All clone instances reside in classes with the same grandparent class.
        \item \textbf{Same Hierarchy}: All clone instances are part of the same inheritance hierarchy.
    \end{itemize}
    \item \textbf{Common Interface}: All clone instances are in classes that have the same interface.
    \begin{itemize}
        \item \textbf{Same Direct Interface}: All clone instances are in a class that have the same interface.
        \item \textbf{Same Class}: All clone instances are in an inheritance hierarchy that contains the same interface.
    \end{itemize}
    \item \textbf{Unrelated}: All clone instances are in classes that have the same interface.
    \begin{itemize}
        \item \textbf{No Direct Superclass}: All clone instances are in classes that have the Object class as parent.
        \item \textbf{No Indirect Superclass}: All clone instances are in a hierarchy that contains a class that has the Object class as parent.
        \item \textbf{External Superclass}: All clone instances are in classes the same external class as parent.
        \item \textbf{Indirect External Ancestor}: All clone instances are in a hierarchy that contains a class that has an external class as parent.
    \end{itemize}
\end{itemize}
Based on these relations, we determine where to place the cloned code when refactored. The code of clones that have a \textit{Common Class} relation can be refactored by placing the cloned code in this same class. The code of clones with a \textit{Common Hierarchy} relation can be placed in the intersecting class in the hierarchy (the class all clone instances have in common as an ancestor). The code of clones with a \textit{Common Interface} relation can be placed in the intersecting interface, but in the process has to become part of the classes' public contract. The code of clones that are \textit{Unrelated} can be placed in a newly created place: either a utility class, a new superclass abstraction or an interface.
